### 2018-04-13 ident/docs/draft_2.tex
changes to section 2 of results

	\subsection{Degree of identifiability of different enzyme kinetic rate laws}\label{sec:ident_rate_laws}	
	In Figure \ref{fig:ident} and Supplementary Figure \ref{fig:ident_root2}, we show the number and percentage of experimental data combinations that are capable of identifying each parameter in each of the four fluxes $v_1$ (Figure \ref{fig:ident}a and e), $v_2$ (Figure \ref{fig:ident}b and f), $v_3$ (Figure \ref{fig:ident}c and g) and $v_5$ (Figure \ref{fig:ident}d and h) belonging to the network shown in Figure \ref{fig:network}. Based on the definition given in Section \ref{sec:degree_of_identifiability}, the percentages refer to the degree of identifiability of each parameter. We see from Figure \ref{fig:ident} and Supplementary Figure \ref{fig:ident_root2} that the degree of identifiability of the maximum reaction rates ($V_i^{max}$), whenever they are identifiable for each of the four fluxes, is greater than or equal to the degree of identifiability of the corresponding enzyme binding ($K_i$) constants, or the allosteric activation constant ($K_3^{pep}$), in the respective reaction rate law models. We make this observation despite the fact that the four fluxes are modeled using three different enzyme kinetic rate laws: $v_1$ and $v_2$ are modeled using the Michaelis-Menten rate law, $v_3$ is modeled using the Convenience Kinetic rate law, and $v_5$ is modeled as a Hill equation with inhibition. We accordingly surmise that the maximum reaction rate parameters are always more identifiable (as indicated by their higher degree of identifiability) than their enzyme binding constant counterparts, irrespective of the enzyme kinetic rate law used to model the corresponding flux.

	In Figures \ref{fig:ident}a and \ref{fig:ident}e less than 50\% of all data combinations can identify $v_1$. Whereas, all available data combinations satisfy the requirements for identifying $v_2$ (Figures \ref{fig:ident}b and f). This observation is true when data from either the MWC model (Figures \ref{fig:ident}a and b) or the Convenience kinetics model for $v_3$ (Figures \ref{fig:ident}e and \ref{fig:ident}f) is used. This difference can be alluded to the ability of data from different combinations of experiments to satisfy the conditions determined for practical identifiability of that parameter. For example, we showed in Equation (\ref{eq:v1_par}) that for a combination of any two experiments to be capable of identifying $V_1^{max}$ and $K_1^{ac}$ in $v_1$, the experiments must have distinct acetate concentrations as well as a different uptake flux $v_1$ between them. So, in this instance, the ability of a combination of experiments to be useful is determined by the ability of the input change (changes in the input acetate concentration) to effect a change in the measured value of $v_1$. Similarly, the identification of parameters for $v_2$ (Figure \ref{fig:ident}b) requires the experiments to distinguish between values of both $v_2$ as well as \textit{pep}.

	In addition to the observation on the degrees of identifiability of different parameter types, we also see that the enzyme kinetic rate law used to model a flux determines the ability to identify the parameters within the given model. For instance, as we state in the Methods section, we could not apply our methodology to determine closed form solution for all the parameters when $v_3$ is modeled using MWC kinetics. In contrast, when $v_3$ is modeled using the Convenience Kinetic rate law, we find that the parameters are locally identifiable based on the definition we provide in section \ref{sec:ident}. We say locally identifiable due to the fact that all three parameters $V_3^{max}$, $K_3^{fdp}$ and $K_3^{pep}$ have two possible roots. In Figure \ref{fig:ident}c, we only show one of the two roots for each parameter in $v_3$. The identifiability of parameters based on the second root obtained from the computer algebra system are shown in Figure \ref{fig:ident_root2}b.

>>>>

	\subsection{Degree of identifiability of different enzyme kinetic rate laws}\label{sec:ident_rate_laws}	
	In Figure \ref{fig:ident} and Supplementary Figure \ref{fig:ident_root2}, we show the number and percentage of experimental data combinations that are capable of identifying each parameter in each of the four fluxes $v_1$ (Figure \ref{fig:ident}a and e), $v_2$ (Figure \ref{fig:ident}b and f), $v_3$ (Figure \ref{fig:ident}c and g) and $v_5$ (Figure \ref{fig:ident}d and h) belonging to the network shown in Figure \ref{fig:network}. Based on the definition given in Section \ref{sec:degree_of_identifiability}, the percentages refer to the degree of identifiability of each parameter. We see from Figure \ref{fig:ident} and Supplementary Figure \ref{fig:ident_root2} that the degree of identifiability of the maximum reaction rates ($V_i^{max}$), whenever they are identifiable for each of the four fluxes, is greater than or equal to the degree of identifiability of the corresponding enzyme binding ($K_i$) constants, or the allosteric activation constant ($K_3^{pep}$), in the respective reaction rate law models. We make this observation despite the fact that the four fluxes are modeled using three different enzyme kinetic rate laws: $v_1$ and $v_2$ are modeled using the Michaelis-Menten rate law, $v_3$ is modeled using the Convenience Kinetic rate law, and $v_5$ is modeled as a Hill equation with inhibition. This observation is also true irrespective of the kinetic rate law used to model $v_3$ (MWC vs Convenience kinetics) to generate in silico experimental data. We accordingly surmise that the maximum reaction rate parameters are always more identifiable (as indicated by their higher degree of identifiability) than their enzyme binding constant counterparts, irrespective of the enzyme kinetic rate law used to model the corresponding flux.

	When data based on the MWC model for $v_3$ is used for identifying parameters, less that 50\% of all data combinations can identify $v_1$ (Figure \ref{fig:ident}a). Even though the degree of identifiability of $K_1^{ac}(ne)$ is significantly different when data derived from the Convenience kinetics model for $v_3$ is used for identification (Figures \ref{fig:ident}e), the degree of identifiability is still less that 50\% for both parameters. In contrast, all available data combinations (from the MWC model and the Convenience kinetics model) satisfy the requirements for identifying $v_2$ (Figures \ref{fig:ident}b and f).

	The difference in the degrees of identifiability between $v_1$ (Figure \ref{fig:ident}a) and $v_2$ (Figure \ref{fig:ident}b) can be attributed to the ability of data from different combinations of experiments to satisfy the conditions determined for practical identifiability of that parameter. To elaborate, we showed in Equation (\ref{eq:v1_par}) that for a combination of any two experiments to be capable of identifying $V_1^{max}$ and $K_1^{ac}$ in $v_1$, the experiments must have distinct acetate concentrations as well as a different uptake flux $v_1$ between them. So, in this instance, the ability of a combination of experiments to be useful is determined by the ability of the input change (changes in the input acetate concentration) to effect a change in the measured value of $v_1$. Similarly, the identification of parameters for $v_2$ (Figure \ref{fig:ident}b) requires the experiments to distinguish between values of both $v_2$ as well as \textit{pep}.

	The difference in the degree of identifiability of $v_1$ that comes about from the use of experimental data from different rate law models used to model $v_3$ (Figures \ref{fig:ident}a and e) can be again attributed to the usefulness of experimental data. However, the difference in data usefulness between similar experiments due to differences in the kinetic rate law used for $v_3$ could be due to the difference in the dynamics of the network represented by either of the two models. The difference in dynamics in turn contributes to different experimentally observed values of metabolite concentrations and fluxes (Figure \ref{fig:experimental_data_dist}), which in turn changes the usefulness of the given combination of datasets and its subsequent effect of parameter identifiability. Nonetheless, we would like to note that these differences in the dynamics contributed by the difference between the rate laws can be resolved with more information i.e., experimental proteomic data that provide protein concentrations for different experiments. We earlier saw that relaxing the assumption on the available experiment data, i.e., assuming the availability of protein concentration (\textit{E}), in addition to the metabolite concentrations (\textit{pep} and \textit{fdp}) and fluxes, results in removal of uncertainty and global identifiability of $v_1$ (Supplementary Figure \ref{fig:parameter_value_proof}). Additionally, we also see an improvement in the degree of identifiability of the corresponding parameters $k_1^{cat}$ and $K_1^{ac}$ (Supplementary Figure \ref{fig:ident_root2}) when enzyme concentrations are available.

	We would also like to point out that a difference in either the ability to estimate true parameter values, or the the identifiability of parameter modeling $v_2$ does not arise due to difference in the kinetic models used to obtain in silico experimental data. This could because of the fact that any and all available information that is required for the identification of parameters in $v_2$ is encompassed in the steady state data used for identifiability analysis.

	 In contrast, when $v_3$ is modeled using the Convenience Kinetic rate law, we find that the parameters are locally identifiable based on the definition we provide in section \ref{sec:ident}. We say locally identifiable due to the fact that all three parameters $V_3^{max}$, $K_3^{fdp}$ and $K_3^{pep}$ have two possible roots. In Figure \ref{fig:ident}c, we only show one of the two roots for each parameter in $v_3$. The identifiability of parameters based on the second root obtained from the computer algebra system are shown in Figure \ref{fig:ident_root2}b.
